Unsupervised Acquisition of Comprehensive Multiword Lexicons \\ using Competition in an $n$-gram Lattice

### 2017-01-20 tacl.tex
typos and removed unused texts

%\eaclfinalcopy % Uncomment this line for the final submission
%\def\eaclpaperid{***} %  Enter the acl Paper ID here

%\setlength\titlebox{5cm}
% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.

@@

%We use the term \termdef{collocation} to refer to statistical co-occurrence without necessarily any lexicalization of the sort implied by our definition of FS. 
% TJB: I'd suggest staying away from talking about collocations altogether: it's an overloaded term; many MWEs are *not* collocations under this definition; and it's not needed for this paper
%MWEs are a non-compositional subset of FS, and they overlap with named entities (NEs). In this regard, we disagree with the MWE annotation schema of \newcite{Schneider14a} which includes any NE as an MWE, which, in the context of product reviews from the Web Treebank, means that that named entities form nearly 50\% of the MWEs types attested in that corpus, with many being phrases such as \ex{Tintman Nationwide Tints Ltd} or \ex{Hickory Furniture Mart} which are easily identifiable as NEs based on their form, but would not be considered part of the mental lexicon of even a tiny fraction of English speakers.% (not even, we might argue, most of these people who work for these businesses, they likely refer to them using shorter, informal names). 
% TJB: too subtle/controversial a point for this paper
%The upshot of this choice that a significant portion of ``MWE'' identification in the dataset is in fact named entity recognition. Some well-known named entities are obviously good MWEs (\eg \ex{George Washington}, \ex{the United States}), but not the names of the vast majority of people, businesses, or products which have real-word referents; they do not belong in a lexicon of formulaic sequences which is intended to reflect the internal lexicon of (at least) a significant generalizable subset of English speakers, putting them outside the scope of this work.

@@

%Unlikely with true MWEs there is no other single necessary condition for some collection of words to be a formulaic sequence, but there are many indicators: Wray \shortcite{Wray08} lists 11 diagnostic criteria, including exact repetition, a lack of semantic transparency, genre associations, pragmatic effects, non-standard syntax, statistical irregularity, and phonological properties. We also want to distinguish FS from collocations, which are

%Wray's conception of formulaic language is explicitly not that of mere exception to the combinatorial creativity of syntax and semantics; she argues that most language can be viewed to some degree as formulaic, and that the use of formulaic sequences is the default mode for most genres, both written and oral. Moreover, her view is that the processing of language in general should be viewed not so much as a bottom-up construction of larger phrases from individual lexical units, but rather as a top-down process where larger chunks are split apart and analyzed as discrete parts only when there is clear evidence for flexibility, a strategy that has a direct analogy in the decomposition approach used here. Another important aspect of the theory is a focus on the linear sequence rather than some other kind of syntactic abstraction (\eg a dependency relationship) as being primary to the internal representation of multiword phenomena, a perspective which allows for much cleaner analysis of longer and more varied expressions: when cases of sequence-internal flexibility occur, they are handled by the inclusion of a slot or gap which is also part of the sequence. Note that, since humans are fairly skilled at interpreting noisy input of various kinds, the notion of sequence as the default glue of the internal multiword lexicon does not rule out the possibility of greater creativity (\eg reversing word order), but this should be understood as the speaker abandoning one of the benefits of formulaic sequences (easy processing) for other communicative purposes (\eg humor).

%Second language acquisition is one of the major areas of application for work on formulaic sequences \cite{Ellis08}. Wray \shortcite{Wray08} posits that the difficulty many adult second language learners have reaching fluency reflects, at least in part, an inattention to the role of formulaic sequences, coupled with an expectation that a language should allow for free combination of words governed only by the basic rules of syntax. Modern communicative approaches to teaching tend to encourage learners to express themselves freely so long as they are able to make themselves understood, \ie to satisfy the short-term communicative goal. However, if full fluency and social integration into the culture of native speakers is a long-term goal, as it is for many immigrant learners for instance, these learners also need to correctly process and eventually produce a wide range of formulaic sequences. Creating high-coverage vocabularies based on real, modern language usage is a first step in helping learners with these challenging but ubiquitous units of language.

@@

%The starting assumption for this work is that given a large corpus, a fairly low $n$-gram frequency threshold, and an extraction technique which allows for non-contiguous $n$-grams, we can collect a set of initial $n$-grams types which include a significant portion of the formulaic sequences (FS) that we can reasonably hope to identify in such a corpus; of course, the resulting vocabulary will be specific to the language, genre and domain, and there will be insufficient statistics to identify FS that are extremely rare in the corpus. Our method for FS extraction assumes such a initial set of $n$-grams, and focuses on identifying the true FS, and excluding those sequences which can be explained away due to the syntax of the language and/or the existence of other FS. The former can be captured to some extent using a syntax-sensitive association measure like LPR, but the latter requires a full, iterative model, where $n$-grams in essence complete with each other to form a compact, parsimonious formulaic vocabulary.

@@

% Some sample minLPR values are given in Table XXXXX (???).

@@

The central process of the model is to decide which nodes in an $n$-gram lattice correspond to an FS, based on the objective of minimizing the overall explanatory power of the lattice. Like probabilities, explainedness of individual nodes will vary between 0 and 1, with 1 corresponding to a node which is fully explained. It will be useful to define the explainedness of a node in terms of two functions: the rationale for having two functions is that the on/off status of a node completely changes the influence that surrounding nodes will have: when a node is off, it is generally desirable (or at least not undesirable) that connected nodes in the lattice are on, since they may serve to partially or entirely explain its existence. When a node is on, however, the presence of other turned-on nodes nearby suggests redundancy, and is not to be encouraged. Let $E_{1}$ be the explainedness of a node when it is on, corresponding to an $n$-gram which has been identified as an FS, and $E_{0}$ be the explainedness of a node when it off. The base value of $E_{0}$ is the inverse of the minLPR metric discussed above: when the minLPR metric is 1, corresponding to a case when the syntactic content predicts one of the words of the $n$-gram as well or better than the lexical context, $E_{0}$  will also be 1. The base value of $E_{1}$ is the inverse of a cost parameter $C$ and, for nodes not influenced by one of the other factors discussed below, is equivalent to the initial threshold for building a vocabulary using the minLPR association measure: all else being equal, when $minLPR(t) > C$, a node will be selected as an FS. There is no necessary upper bound on $C$, but we note here that there is a fairly small range of good choices for $C$; we have found that setting it too high ($>6$, corresponding to minimum of six times more likely than predicted by POS context alone) will restrict the model primarily to sequences with only open-class words, while setting it too low ($<3$) allows in too much random noise.

%Most of these modulations we use here are related to the node interactions discussed below, but we begin by introducing a simple example of a modulation which uses the $n$-gram count.

@@

%LPR is a association measure based on conditional probability, and therefore tends to underestimate the importance of marginal probability, missing common expression formed using high frequency words. As such, it is common for more complex association measures to include multiplication by the count, or logarithm of the count. In the context of this model, multiplying our cost by even the logarithm of the count would be far too extreme, but we can give apply a more restricted increase to $C_0$, forcing the model to give more weight to relatively common expressions, as follows: Let $c(\dot)$ be the count function, and $c(min)$ and $c(max)$ refer to the lowest and highest count $n$-gram in the lattice (not including unigrams).

%\begin{displaymath}
%d_0(t) = 1 + \frac{\log\frac{c(t)}{c(min)}}{\log\frac{c(max)}{c(min)}}
%\end{displaymath}

%This logarithmically scales the count into the range of 0 and 1; the $C_0$ of $n$-grams at the cutoff will be unaffected ($mod(t) = 1$) , while the maximum value of $d_0$ results in a squaring of the initial LPR-ratio.

@@

%Another source of error are somewhat flexible FS which fall below our $n$-gram threshold but where some portion of the FS is above the threshold: to address this, we collect additional statistics and remove as a post-processing step any FS which are hard covered by an $n$-gram not in our lattice.

@@

%The algorithm for optimization procedure is given in Figure X (???).

@@

% For these test sets, we report (in Table 1) inter-annotator agreement in terms of average $f$-score across annotators, which is appropriate for highly-imbalanced class situations such as this (formulaic is considered the positive class for this and other calculations), and also provides a human upper bound.

%In addition, we also test the ICWSM-derived lexicon against the ``MWE'' test set from Brooke et \al \shortcite{Brooke15b} whose $n$-gram annotations (both gappy and non-gappy) are derived from the MWE annotation of Schneider \shortcite{Schneider14b}.

@@

%Otherwise, gaps in MWEs have generally addressed by using full syntactic representations \cite{Seretan11}.
%One more restriction is necessary to make the use of overlaps feasible: without any restrictions, the number of connections resulting from overlaps is too large. We resolved this problem by excluding as possible active nodes.

%a separate analysis of the that corpus showed the contents of most gapped FS in English were simple nouns or some portion thereof; this is somewhat less true for the more free word-order langauges we are also considering, but still a usuable heuristic.

%which be described by the following (Penn Treebank) POS regular expression:

%\vspace{3mm}
%\noindent
% PP$\,$|$\,$[(PDT)(DT)JJ*[NN$\,$|$\,$NP]*(POS$\,$|$\,$PP\$)JJ*NN*]
%\vspace{1mm}

%(Our POS tags are given by the TreeTagger)

% For our main evaluation in English, our corpus is a 890 million version of the tier 1 texts in the ICWSM 2009 blog corpus \cite{ICWSM} which has been filtered to remove duplicates and near duplicates.
\bibliography{mybib}
\bibliographystyle{acl2012}

>>>>

@@

@@

@@

@@

@@

The central process of the model is to decide which nodes in an $n$-gram lattice correspond to an FS, based on the objective of maximizing the overall explanatory power of the lattice. Like probabilities, explainedness of individual nodes will vary between 0 and 1, with 1 corresponding to a node which is fully explained. It will be useful to define the explainedness of a node in terms of two functions: the rationale for having two functions is that the on/off status of a node completely changes the influence that surrounding nodes will have: when a node is off, it is generally desirable (or at least not undesirable) that connected nodes in the lattice are on, since they may serve to partially or entirely explain its existence. When a node is on, however, the presence of other turned-on nodes nearby suggests redundancy, and is not to be encouraged. Let $E_{1}$ be the explainedness of a node when it is on, corresponding to an $n$-gram which has been identified as an FS, and $E_{0}$ be the explainedness of a node when it off. The base value of $E_{0}$ is the inverse of the minLPR metric discussed above: when the minLPR metric is 1, corresponding to a case when the syntactic content predicts one of the words of the $n$-gram as well or better than the lexical context, $E_{0}$  will also be 1. The base value of $E_{1}$ is the inverse of a cost parameter $C$ and, for nodes not influenced by one of the other factors discussed below, is equivalent to the initial threshold for building a vocabulary using the minLPR association measure: all else being equal, when $minLPR(t) > C$, a node will be selected as an FS. There is no necessary upper bound on $C$, but we note here that there is a fairly small range of good choices for $C$; we have found that setting it too high ($>6$, corresponding to minimum of six times more likely than predicted by POS context alone) will restrict the model primarily to sequences with only open-class words, while setting it too low ($<3$) allows in too much random noise.

@@

@@

@@

@@

@@

\bibliography{mybib}
\bibliographystyle{acl2012}
